The Effects of the 2023 Rule Changes in Major League Baseball

### 2023-11-10 manuscript/paper.tex
added code for table in code folder, added the table to manuscript also

\doublespacing

@@

All ten questions can be tested using a standard two-sample comparison with the \(t\)-test.
The \(z\)-test was considered as done in \citet{Price}, but we do not know the population standard deviation
in this case. The \(t\)-test assumes the data is normally distributed so to account
for this, we also conducted the nonparametric, distribution free, Mann Whitney U
Test (also known as the Wilcoxon Rank Sum Test) to be sure of our results. Also,
notice how some of these research questions call for a one-sided hypothesis test,
like the number of hits on ground balls, because we intuitively expect this number
to be greater in 2023 than in 2022 due to the limit of the defensive shift. Other
metrics that we were not sure about whether they would increase or decrease were
tested using a two-sided hypothesis test, simply testing for a significance in the
overall difference from season to season. Other methods such as regression were
considered for this study as well, but we are primarily interested in comparing
means and assessing the effect of a single variable, so a \(t\)-test is more appropriate
and straightforward.

@@

Summarize the results.

>>>>

\setlength{\tabcolsep}{10pt}
\doublespacing

@@

All ten questions can be tested using a standard two-sample comparison with the \(t\)-test.
The \(z\)-test was considered as done in \citet{Price}, but we do not know the population standard deviation
in this case. The \(t\)-test assumes the data is normally distributed so to account
for this, we also conducted the nonparametric, distribution free, Mann Whitney U
Test (also known as the Wilcoxon Rank Sum Test) to be sure of our results.

Also, notice how some of these research questions call for a one-sided hypothesis test,
like the number of hits on ground balls, because we intuitively expect this number
to be greater in 2023 than in 2022 due to the limit of the defensive shift. Other
metrics that we were not sure about whether they would increase or decrease were
tested using a two-sided hypothesis test, simply testing for a significance in the
overall difference from season to season. Other methods such as regression were
considered for this study as well, but we are primarily interested in comparing
means and assessing the effect of a single variable, so a \(t\)-test is more appropriate
and straightforward.

@@

Insert description about Table~\ref{tab:table1} here.

\begin{table}[tbp]
  \caption{The results from the 9 tests}
  \label{tab:table1}
  \centering
  \begin{tabular}[t]{lccccc}
    \toprule
    & 2023 & 2022 & \multicolumn{2}{c}{P-value}\\
    \cmidrule(lr){4-5}
    &          &                & \(t\)-test & Wilcoxon's\\
    \midrule
    Stolen Bases & 7.226 & 4.994 & 0.0000 & 0.0011 \\ 
    Strikeouts & 85.445 & 81.731 & 0.1596 & 0.0000 \\ 
    Walks & 32.876 & 30.279 & 0.0599 & 0.0791 \\ 
    Batting Avg & 0.243 & 0.237 & 0.0274 & 0.0154 \\ 
    Slugging \% & 0.401 & 0.384 & 0.0008 & 0.0007 \\ 
    BABIP & 0.293 & 0.288 & 0.0793 & 0.0695 \\ 
    xBA & 0.241 & 0.235 & 0.0006 & 0.0005 \\ 
    Hits on GB & 27.345 & 26.399 & 0.3757 & 0.3212 \\ 
    GIDP & 7.232 & 6.925 & 0.3523 & 0.5401 \\ 
    \bottomrule
  \end{tabular}
\end{table}
